---
title: "Bonferoni VS Biniamini-Hochebreg"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library("expm")
library("MASS")
```
load the data
```{r}
load("C:/Users/??????/Downloads/meth_dat.rda")
```

t-stat: comparing the means and dividing by SD
```{r}
tstat1 <- function(y,colonind,lungind){
t1 <- (colMeans(y[colonind,])-colMeans(y[lungind,]))/(sqrt(diag(var(y[colonind,]))/length(colonind)+diag(var(y[lungind,]))/length(lungind)))
}

```
convert to Pi
```{r}
t1 <- tstat1(meth_dat,colonind,lungind)
p1 <- 1-pt(abs(t1),34)
sum(p1*2<0.05)
```

wathing the distribution of p
```{r}
hist(p1)
plot(p1)
abline(0.05,0,col="blue")
#H0 might not be true since we have ununiform density
```

Bonferoni
```{r}
# each hypothesis under alpha/B
bonf <- function(num,p){
B1 <- rep(0,num)
for (i in 1:num) {
  if(p[i]<0.025/num){
    B1[i]=1
  }
}
return(B1)
}
B1 <- bonf(1000,p1)
print(sum(B1))
```

Biniamini-Hochebreg
```{r}
#wd dont need to look on every observation
BH=function(p,q=0.05, ret_ind = TRUE){
  a=sort(p)
  n=length(a)
  i=n
  while (a[i]>((i/n)*q) && i>=1){
    i=i-1
  }
  if(ret_ind){
    return(i)
  } else{
    if(i>0){
      return(a[i])
    }
    else{
      return(0)
    }
  }
}
B_H <- BH(p1,0.025)
print(B_H)
```

which hypohesis have been rejected
```{r}
BHD <- p1<=sort(p1)[730]
```
variences
```{r}
#using regularization
cov1 <- var(meth_dat[colonind,])*0.8+0.2/1000*sum(diag(var(meth_dat[colonind,])))*diag(1000)
cov2 <- var(meth_dat[lungind,])*0.8+0.2/1000*sum(diag(var(meth_dat[lungind,])))*diag(1000)
cov1_h <- sqrtm(cov1) #improving processing speed
cov2_h <- sqrtm(cov2)
```
Bootstrap-parametric
```{r}
#H0- we have two distinctive distributions
boot_par <- function(data,vec1,vec2,B,var1,var2){
p_min <- rep(0,B)
  for (i in 1:B) {
  a <- mvrnorm (n=length(vec1),mu=rep(0,1000),Sigma =diag(1000))
  b <- mvrnorm (n=length(vec2),mu=rep(0,1000),Sigma =diag(1000))
  c <- rbind(a%*%var1,b%*%var2)
    t <- tstat1(c,vec1,vec2)
    p<- (1-pt(abs(t),34))*2
p_min[i] <- min(p)
}
p_crit <- (sort(p_min))[0.05*B]
d <- rep(0,1000)
 for (j in 1:1000) {
  if(p1[j]<p_crit){
   d[j] <- 1
  }
 }
return(d)
}
b_par_crit <- function(data,vec1,vec2,B,var1,var2){
p_min <- rep(0,B)
  for (i in 1:B) {
  a <- mvrnorm (n=length(vec1),mu=rep(0,1000),Sigma =diag(1000))
  b <- mvrnorm (n=length(vec2),mu=rep(0,1000),Sigma =diag(1000))
  c <- rbind(a%*%var1,b%*%var2)
    t <- tstat1(c,vec1,vec2)
    p<- (1-pt(abs(t),34))*2
p_min[i] <- min(p)
}
p_crit <- (sort(p_min))[0.05*B]
return(p_crit)
}
```
Calculate results
```{r}
pb_rejc <- boot_par(meth_dat,colonind,lungind,1000,cov1_h,cov2_h)
print(sum(pb_rejc))
```

p-crit of bootstrap-parametric
```{r}
bp_crit <- b_par_crit(meth_dat,colonind,lungind,1000,cov1_h,cov2_h)
```


function that generate non parametric data-subtracting means and taking samples from rows.
```{r}
gen_non_par = function(n,mu, orig_dat){
  nn=dim(orig_dat)[1]
  pp=dim(orig_dat)[2]
  norm_orig_dat=orig_dat-matrix(rep(mu,each = nn),nrow = nn,ncol=pp)  
  inds = sample(nn,n, replace = TRUE)
  return(as.matrix(norm_orig_dat[inds,]))
}
```
bootstrap non prametric
```{r}
#H0- we have two distinctive distributions
b_n_par <- function(data,vec1,vec2,B){
   p_min <- rep(0,B)
  for (i in 1:B){
  a <- gen_non_par(length(vec1),colMeans(data[vec1,]),data[vec1,])
  b <- gen_non_par(length(vec2),colMeans(data[vec2,]),data[vec2,])
  c <- rbind(a,b)
  t <- tstat1(c,vec1,vec2)
    p<- (1-pt(abs(t),34))*2
p_min[i] <- min(p)
}
p_crit <- (sort(p_min))[0.05*B]
e <- rep(0,1000)
 for (j in 1:1000) {
  if(p1[j]<p_crit){
   e[j] <- 1
  }
 }
return(e)
} 
#t-crit
b_n_par_crit <- function(data,vec1,vec2,B){
     p_min <- rep(0,B)
  for (i in 1:B){
  a <- gen_non_par(length(vec1),colMeans(data[vec1,]),data[vec1,])
  b <- gen_non_par(length(vec2),colMeans(data[vec2,]),data[vec2,])
  c <- rbind(a,b)
  t <- tstat1(c,vec1,vec2)
    p<- (1-pt(abs(t),34))*2
p_min[i] <- min(p)
}
p_critbnp <- (sort(p_min))[0.05*B]
return(p_critbnp)
}

```
calculate
```{r}
nonpar_rej <- b_n_par(meth_dat,colonind,lungind,1000)
sum(nonpar_rej)
#only 71 rejections, really small comparing to bootstrapprametric.Indicate that we have large variance  and problem in Ho of uniform distribution.
```

t_crit
```{r}
bnp_crit <- b_n_par_crit(meth_dat,colonind,lungind,1000)

```

CI function
```{r}
CI <- function(hat,data){
  a <- hat-sqrt(hat*(1-hat)/ncol(data))*1.96
  b <- hat+sqrt(hat*(1-hat)/ncol(data))*1.96
  print(a);print(b)
}

```
Bonferoni on new data
```{r}
bnf <- rep(0,1000)
for (i in 1:1000){
  new_data <- rbind(gen_non_par(length(colonind),colMeans(meth_dat[colonind,]),meth_dat[colonind,]),gen_non_par(length(lungind),colMeans(meth_dat[lungind,]),meth_dat[lungind,]))
  bnf[i]  <- sum(bonf(1000,1-pt(abs(tstat1(new_data,colonind,lungind)),34)))
} 
print(sum(bnf>0)/1000)  #FWER-0.846-huge (we'll check againt 0.05)
```
Bonferoni- CI on new data
```{r}
CI(sum(bnf>0)/1000,meth_dat)
```
BH on new data-FWER
```{r}
BHN <- rep(0,2000)
for (i in 1:2000){
   new_data <- rbind(gen_non_par(length(colonind),colMeans(meth_dat[colonind,]),meth_dat[colonind,]),gen_non_par(length(lungind),colMeans(meth_dat[lungind,]),meth_dat[lungind,]))
  BHN[i] <- BH(1-pt(abs(tstat1(new_data,colonind,lungind)),34),0.025)
}
print(sum(BHN>0)/2000) #FWER is huge
```
BH- CI on new data
```{r}
CI(sum(BHN>0)/2000,meth_dat)
```
bootstrap prametric on new data-FWER 
```{r}
bp_fwer <-rep(0,1000) 
for (i in 1:1000){
 rej1 <- rep(0,1000)
  new_data <- rbind(gen_non_par(length(colonind),colMeans(meth_dat[colonind,]),meth_dat[colonind,]),gen_non_par(length(lungind),colMeans(meth_dat[lungind,]),meth_dat[lungind,]))
   t2 <- tstat1(new_data,colonind,lungind)
    p2<- (1-pt(abs(t2),34))*2
    for (j in 1:1000) {
    
  if(p2[j]<bp_crit){
    rej1[j] <- 1
  }
    }
    bp_fwer[i] <- sum(rej1)
}
sum(bp_fwer>0)/1000 # FWER is huge
```

bootstrap prametric on new data- CI
```{r}
CI(sum(bp_fwer>0)/1000,meth_dat)
```

bootstrap non prametric on new data-FWER & CI
```{r}
#FWER-rejections/hypothesis, var=p*1-p/B because it's bionom distirbution
bnp_fwer <-rep(0,1000) 
for (i in 1:1000){
 rej <- rep(0,1000)
  new_data <- rbind(gen_non_par(length(colonind),colMeans(meth_dat[colonind,]),meth_dat[colonind,]),gen_non_par(length(lungind),colMeans(meth_dat[lungind,]),meth_dat[lungind,]))
   t3 <- tstat1(new_data,colonind,lungind)
    p3<- (1-pt(abs(t3),34))*2
    for (j in 1:1000) {
    
  if(p3[j]<bnp_crit){
    rej[j] <- 1
  }
    }
    bnp_fwer[i] <- sum(rej)
}
mean(bnp_fwer>0) # FWER 
```

```{r}
CI(mean(bnp_fwer>0),meth_dat)

```
```{r}
#CI for min 5 pi
(which(p1==0))[1:5]
var74 <- var(meth_dat[1:17,74])/17+var(meth_dat[18:36,74])/19
var103 <- var(meth_dat[1:17,103])/17+var(meth_dat[18:36,103])/19
var145 <- var(meth_dat[1:17,145])/17+var(meth_dat[18:36,145])/19
var147 <- var(meth_dat[1:17,147])/17+var(meth_dat[18:36,147])/19
var149 <- var(meth_dat[1:17,149])/17+var(meth_dat[18:36,149])/19
m74 <- mean(meth_dat[1:17,74])-mean(meth_dat[18:36,74])
m103 <- mean(meth_dat[1:17,103])-mean(meth_dat[18:36,103])
m145 <- mean(meth_dat[1:17,145])-mean(meth_dat[18:36,145])
m147 <- mean(meth_dat[1:17,147])-mean(meth_dat[18:36,147])
m149 <- mean(meth_dat[1:17,149])-mean(meth_dat[18:36,149])
var_c <- (c(var74,var103,var145,var147,var149))
mu <- c(m74,m103,m145,m147,m149)
ci_l5 <-rep(0,5)
  for (i in 1:5) {
  ci_l5[i] <- mu[i]-sqrt(var_c[i])*qnorm(1-0.025*5/1000)
  
  }
ci_h5 <-rep(0,5)
  for (i in 1:5) {
  ci_h5[i] <- mu[i]+sqrt(var_c[i])*qnorm(1-0.025*5/1000)
  
  }
ci5 <- cbind(ci_l5,ci_h5)
print(ci5)
```
table of rejections
```{r}
table_rej <- matrix(c(487,730,522,71),1,4)
colnames(table_rej) <- c("bonferoni","BH","bootsrap_par","bootsrap_non_per")
print(table_rej)
#we can see huge diffrences, meaning we have big covarience
```
